\fact $p(x)$ is separable \emph{iff} $\gcd(p,p')=1$. \\
\defn Let $L/K$ be a field extension, $\alpha\in L$ an algebraic element.  Then $\alpha$ is separable over $K$ \emph{iff} the minimal polynomial for $\alpha/K$ is separable.  We say $L/K$ is separable \emph{iff} every $\alpha\in L$ is separable over $K$. \\
\defn A field $K$ is perfect \emph{iff} every finite extension of $K$ is separable. \\
\thm If $\Char K=0$, then $K$ is perfect. \\
\pf Let $L/K$ be an extension, $\alpha\in L$ an algebraic element, $p(x)\in K[x]$ its minimal polynomial over $K$.  Then $p(x)$ is irreducible in $K[x]$.  If $\alpha\in K$, then $\alpha$ is trivially separable over $K$. \\
If not, then $p'(x)$ is non-constant, of degree smaller than $\deg(p)$.  So $\deg(\gcd(p,p'))<\deg(p)$.  Since $p$ is irreducible, we conclude $\gcd(p,p')=1$. \qed \\
%$(x^7)'=7x^6=0$ in $(\Z/7\Z)[x]$. \\
What kind of polynomial has $0$ derivative?  Say $\Char K=l$.
%in $\Z/3\Z$, $0\neq x^3-x$
\begin{align*}
p(x) &= a_0 + a_1 x + \dotsb + a_n x^n \\
\implies p'(x) &= a_1 + 2 a_2 x + \dotsb + n a_n x^{n-1}
\end{align*}
If $p'=0$ then $ia_i=0$ for all $i$.  This is equivalent to demanding $a_1=0$ for all $i$ prime to $p$. \\
So $p'(x)=0$ \emph{iff}
\[ p(x) = a_0 + a_l x^l a_{2l} x^{2l} + \dotsb + a_{nl} x^{nl} \]
\defn Let $K$ be a field of characteristic $l\neq0$.  Define the Frobenius homomorphism
\[ \Frob_l\colon K\to K \]
by $\Frob_l(a)=a^l$. \\
\thm If $\Char K=l\neq0$, then $(a+b)^l=a^l+b^l$ for all $a$, $b\in K$. %\\
%\pf $(a+b)^l=\sum_{i=0}^l\binom{l}{i}a^ib^{l-i}$ \\
\begin{flalign*}
\pf && (a+b)^l &= \sum_{i=0}^l\binom{l}{i}a^ib^{l-i} && \\
\shortintertext{If $i\neq0,l$, $\binom{l}{i}=\frac{l!}{(l-i)!i!}$ is divisible by $l$, so:}
%\[ = a^l + b^l \qed \]
&& &= a^l + b^l \qed &&
\end{flalign*}
\thm Let $K$ be a field of characteristic $l\neq0$.  Then $K$ is perfect \emph{iff} $\Frob_l\colon K\to K$ is onto (is an isomorphism). \\
\pf Backwards: Assume $\Frob_l$ is onto, and let $\alpha$ be any algebraic element in an extension $L/K$.  Let $p(x)$ be a minimal polynomial for $\alpha/K$.

If $p'(x)\neq0$, then $\gcd(p,p')=1$, and so $\alpha$ is separable over $K$.  If $p'(x)=0$, then:
\begin{align*}
p(x) &= a_0 + a_l x^l + \dotsb + a_{nl}x^{nl} \\
%\footnote{since $\Frob_l$ is onto}
\mathllap{\text{\small(since $\Frob_l$ is onto) }} &= (b_0)^l + (b_1)^l x^l + \dotsb + (b_n)^l x^{nl} \\
&= (b_0+b_1x+\dotsb+b_nx^n)^l
\end{align*}
which is reducible.  This is impossible, so $p'\neq0$.

Forwards: Since $\Frob_l$ is not onto, there is some $a\in K$ such that $a\neq b^l$ for any $b\in K$.  Consider $x^l-a$, and let $F/K$ be a splitting field for $x^l-a$.  There is some root $\alpha\in F$ of $x^l-a$:
\begin{gather*}
\alpha^l - a = 0 \\
\implies x^l - a = x^l - \alpha^l = (x-\alpha)^l
\end{gather*}
Since $\alpha\notin K$, its minimal polynomial $p(x)$ over $K$ has degree at least $2$, and it's a factor of $(x-\alpha)^l$.  So $p(x)$ isn't separable. \qed

\thm Every finite field is perfect. \\
\pf $\Frob_l$, on a finite field is a 1--1 function from a finite set to itself.  It's therefore onto. \qed \\
\eg $\F_l(T)$ is imperfect, since $T$ is not the $l$th power of any rational function, for degree reasons.
\begin{align*}
\C(x) &= \set[\big]{\tfrac{p(x)}{q(x)}}{\substack{p,q\in\C[x]\\q\nequiv0}} \\
\F_l(T) &= \set[\big]{\tfrac{p(T)}{q(T)}}{\substack{p,q\in\F_l[T]\\q\nequiv0}}
\end{align*}
\defn Let $L/K$ be a finite extension.  The separable closure of $K$ in $L$ is the set of all elements of $L$ that are separable over $K$.  %It's written $K^\text{sep}$. 
\\
\thm The separable closure of $K$ in $L$ is a field. \\
\pf Let $K^\text{sep}$ be the separable closure of $K$ in $L$.  Let $\alpha$, $\beta\in K^\text{sep}$ be elements.
\[ \xymatrix{
&K(\alpha,\beta)\ar@{-}[rd]\ar@{-}[ld]&\\
K(\alpha)&&K(\beta)\\
&K\ar@{-}[ru]\ar@{-}[lu]&
} \]
