Recall: Let $f(x)=x^3+x^2-2x+8$ is irreducible over $\Q$.  Let $\theta$ be a root of $f$.  Put $K=\Q(\theta)$.  We have $\disc(\theta)=-R(f,f')=-4\cdot503$.

Let $\theta=\theta_1$, $\theta_2$, $\theta_3$ be the conjugates of $\theta$.  We can check that
\[ g(x) = \prod_{i=1}^3\paren[\Big]{x-\frac{\theta_i^2+\theta_i}{2}} \]
is in $\Z[x]$.  Thus $\frac{\theta^2+\theta}{2}$ is an algebraic integer.  Then $\disc(1,\theta,\frac{\theta^2+\theta}{2})=-503$.  Thus $1$, $\theta$, $\frac{\theta^2+\theta}{2}$ is an integral basis for $K$ since $503$ is squarefree and $\disc(K)=-503$.

The question still remains: \emph{is there} an integral power basis for $K$?  In other words, is there $\lambda\in\A\cap K$ such that $1$, $\lambda$, $\lambda^2$ is an integral basis?

Suppose we have such a $\lambda$.  Then there exist integers $a$, $b$, and $c$ so that
\[ \lambda = a + b\theta + c\paren[\Big]{\frac{\theta^2+\theta}{2}} \]
but then
\[ \lambda^2 = A + B\theta + C\paren[\Big]{\frac{\theta^2+\theta}{2}} \]
where $A=(a^2-2c^2-8bc)$, $B=(-2c^2+2ab+2bc-b^2)$, and $C=(2b^2+2ac+c^2)$.  Note
\[ \begin{pmatrix}1\\
\lambda\\
\lambda^2
\end{pmatrix} = \begin{pmatrix}
1 & 0 & 0 \\
a & b & c \\
A & B & C
\end{pmatrix} \begin{pmatrix}
1 \\
\theta \\
\frac{\theta^2+\theta}{2}
\end{pmatrix} \]
so
\[ \disc(\lambda) = \paren*{\det\begin{pmatrix}
1&0&0\\
a&b&c\\
A&B&C
\end{pmatrix}}^2\disc\paren[\Big]{1,\theta,\frac{\theta^2+\theta}{2}} = \begin{pmatrix}
1&0&0\\
a&b&c\\
A&B&C
\end{pmatrix}\cdot(-503) . \]
But
\begin{align*}
\paren*{\det\begin{pmatrix}
1&0&0\\
a&b&c\\
A&B&C
\end{pmatrix}}^2 &= (bC-Bc)^2 \\
&= (2b^3-bc^2+b^2c+2c^3)^2 \\
&\equiv (b^2c-2bc^2)^2 \bmod 2 \\
&\equiv (bc(b-c))^2 \bmod 2 \\
&\equiv 0 \bmod 2
\end{align*}
Thus $\disc(\lambda)\neq-503$ and so no integral power basis exists.

%missing
$[K:\Q]<\infty$.  An element $\alpha$ in $\A\cap K$ which is not zero and not a unit is said to be an irreducible of $\A\cap K$ if whenever $\alpha=\beta\gamma$ with $\beta$ and $\gamma$ in $\A\cap K$ then $\beta$ is a unit or $\gamma$ is a unit.  We've seen that we don't
have unique factorization into irreducibles up to units and reordering in $\A\cap\Q(\sqrt{-5})$.
%missing
up to units and reordering in $\A\cap\Q(\sqrt{-5})$.

To recover unique factorization we pass to prime ideals in the ring.

Recall that an ideal $P$ in a commutative ring with identity is a prime ideal $\iff$ whenever $ab\in P$ with $a$, $b\in R$ then $a\in P$ or $b\in P$.  Also an integral domain is a commutative ring with identity with no zero divisors.

Suppose $R$ is a subfield of a ring $S$.  Then $\theta$ in $S$ is said to be integral over $R$ if it is the root of a monic polynomial with coefficients in $R$.  $R$ is integrally closed in $S$ if whenever $\theta\in S$ is integral over $R$ then $\theta\in R$.

\defn A Dedekind domain $R$ is an integral domain for which
\begin{enumerate}
\item Every ideal in $R$ is finitely generated.
\item Every non-zero prime ideal in $R$ is maximal
\item $R$ is integrally closed in its field of fractions.
\end{enumerate}
\textbf{Proposition 37:} Let $[L:\Q]<\infty$.  Let $I$ be a non-zero ideal in $\A\cap K$.  There is a positive integer in $I$. \\
\pf Since $I$ is non-zero there exists an $\alpha\in I$ with $\alpha\neq0$.  Let $\alpha=\alpha_1$, $\dotsc$, $\alpha_n$ be the conjugates of $\alpha$ over $\Q$.  Then
\[ N_\Q^{\Q(\alpha)}(\alpha) = \alpha_1\dotsm\alpha_n = a \in \Z\setminus\brace0 . \]
Observe that $\alpha_2\dotsm\alpha_n=a/\alpha_1\in K$.  Further $\alpha_2$, $\dotsc$, $\alpha_n$ are algebraic integers so $\alpha_2$, $\dotsc$, $\alpha_n\in\A$.  Thus $\alpha_2\dotsm\alpha_n\in\A\cap K$.  Thus $(\alpha_1)\cdot(\alpha_2\dotsm\alpha_n)\in I$ so $a\in I$.  But $-a\in I$ also.

\defn Let $[K:\Q]<\infty$ and let $I$ be a non-zero ideal in $\A\cap K$.  Then $\brace{\alpha_1,\dotsc,\alpha_n}$ is an integral basis for the ideal if $\alpha_1$, $\dotsc$, $\alpha_n$ are in $I$ and every element of $I$ has a unique representation as an integral linear combination of $\alpha_1$, $\dotsc$, $\alpha_n$.